Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
Pass on Section 7
pass on discussion of bug in Hermes

Overall, we noted that test transplantation and differential testing
were effective techniques in revealing potential bugs in non-trivial
JavaScript engines of varying degrees of maturity. We found bugs both
in extremely robust and largely adopted engines and also in recently
developed engines. \Mar{check $\rightarrow$}The issue diagnosis of
developers seem to differ though. Issues reported to stable engines
are more likely to be real bugs---as lots of problems have been
already scrutinized---whereas issues reported to new engines are more
likely to be inconsistencies related to influx development as opposed
to real bugs.

@@

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation.
This is a case of validation of RegExp flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as commented by a maintainer.

>>>>

Overall, we noted that test transplantation and differential testing
were effective techniques in revealing potential bugs in non-trivial
JavaScript engines of varying degrees of maturity. We found bugs both
in extremely robust and largely adopted engines and also in recently
developed engines. The issue diagnosis of
developers seem to differ though. Issues reported to stable engines
are more likely to be real bugs---as lots of problems have been
already scrutinized---whereas issues reported to new engines are more
likely to be inconsistencies related to influx development as opposed
to real bugs.

@@

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa.
The original test case contains a string concatenation.
This is a case of validation of RegEx flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegEx \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as explained by one of their developers.
